---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# MultiNeSS

<!-- badges: start -->
<!-- badges: end -->

\texttt{multiness} implements model fitting and simulation for Gaussian and logistic inner 
product MultiNeSS models for multiplex networks. The package uses
a convex fitting algorithm with fully adaptive parameter tuning, 
including options for edge cross-validation. For more details see [MacDonald et al., (2020)](https://arxiv.org/abs/2012.14409).  
    
## Installation

You can install the development version of \texttt{multiness} from GitHub using

``` r
devtools::install_github("peterwmacd/multiness")
```

## Example

\texttt{multiness} includes an example agricultural trade dataset which is studied in [MacDonald et al., (2020)](https://arxiv.org/abs/2012.14409). It is easy to import and to fit a Gaussian MultiNeSS model with adaptive tuning. 

```{r example}
library(multiness)

# import data
data(agri_trade)
# log transformation for edge weights
A <- log(1+agri_trade)

# model fit
fit <- multiness_fit(A=A,model="gaussian",self_loops=FALSE,
                     tuning="adaptive",tuning_opts=list(penalty_const=3),
                     optim_opts=list(max_rank=100))

# inspect fitted latent space dimensions
# common latent space
fit$d1
# individual latent spaces
fit$d2

```

